---
output: github_document
bibliography: MyBib.bib
---

# Repository for my poster at the Mendelian randomization conference 2019

This poster was prepared using the `posterdown` package [@posterdown]. The design is based on the Better Scientific Poster design by @betterposter. I picked up some tips how to edit the html for the poster from https://github.com/lcolladotor/recount-brain-bog19 .

Here are the steps to recreate the poster.

1. Install the posterdown package and, due to the edits I made to my HTML template file, this version of the bookdown package.

    ```{r, eval=FALSE}
    # remotes::install_github("brentthorne/posterdown") # uncomment on first run
    # remotes::install_github("rstudio/bookdown@364092a") # uncomment on first run
    ```

2. Launch the posterdown Rmd template for the portrait version of the Better Scientific Poster.

    ```{r, eval=FALSE}
    rmarkdown::draft("mr2019-tom-palmer-poster.Rmd", 
                     template = "posterdown_betterport", 
                     package = "posterdown")
    ```

3. Edit the Rmd file with your content.

4. Render the Rmd file to html. This can be achieved either by clicking the Knit button in RStudio or by running (change the file name for your poster's Rmd file).

    ```{r results='hide', warning=FALSE, message=FALSE, error=FALSE}
    rmarkdown::render('mr2019-tom-palmer-poster.Rmd',  encoding = 'UTF-8')
    ```

5. To render on github pages:

    * I copied the html poster and its associated `_files` folder and folder of figures, `Figures`, to the `docs` folder because I prefer enabling github pages for a repo from the docs folder rather than from a separate branch.
    ```{r}
    file.copy("mr2019-tom-palmer-poster.html", 
              "./docs/")
    dir.create("./docs/Figures")
    file.copy("Figures", "./docs/", recursive = TRUE)
    dir.create("./docs/mr2019-tom-palmer-poster_files")
    file.copy("mr2019-tom-palmer-poster_files", "./docs/", recursive = TRUE)
    ```
    * I renamed the html poster file to `index.html` and the files folder to `index_files`.
    ```{r}
    file.rename("./docs/mr2019-tom-palmer-poster.html", 
                "./docs/index.html")
    file.rename("./docs/mr2019-tom-palmer-poster_files",
                "./docs/index_files")
    ```
    * I then enabled github pages for this repository in the repository settings on GitHub.

6. The pdf version of the poster can be generated either by opening the html version in Google Chrome and selecting `Print` then `Save as PDF` through the menus or by using the `chrome_print()` function in the [`pagedown`](https://github.com/rstudio/pagedown) package as follows.

    ```{r}
    pagedown::chrome_print("mr2019-tom-palmer-poster.html")
    ```

    * Note, I find that page and column breaks can be in slightly different positions in the pdf compared to the html.

7. Note that this `README.md` file is generated by knitting `README.Rmd`.

8. For reproducibility, report R session information.

    ```{r}
    # install.packages("sessioninfo") # uncomment on first run
    sessioninfo::session_info()
    ```

## References